### 2025-06-24 manuscripts/10-JERP-v3/manuscript_main.tex
Updates from Overleaf

>>>>

My findings reveal significant penalties associated with Hispanic surnames. Native-born individuals who likely have Hispanic-sounding last names receive 0.39 fewer years of education than their counterparts with White-sounding last names, with particularly pronounced effects in higher education: they are 20\% less likely to earn an associate degree and 22\% less likely to earn a bachelor's degree. In the labor market, those with Hispanic surnames face a 14\% higher unemployment rate and earn 5\% less annually than their peers with White surnames. These disparities are especially pronounced for women, who experience larger gaps in both educational attainment and labor market outcomes, highlighting how ethnic and gender discrimination intersect to compound disadvantages.
